An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-11-21 article.tex
included abstract and minor changes after proof reading

% \begin{abstract}
% \end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

@@

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to support grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \small
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{Number of Classes} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & KGs of Nitrogen & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
\normalsize
The data originally contained only two multiclass variables: year and region. Related binary variables, such as the use of river water and the use of dam water, were combined to create a single multiclass variable. This was done by first converting each combination that occurred into a unique category (such as river and damn water used, as opposed to the two separate categories prior). These variables were then one-hot-encoded, changing each variable class into a binary value, with one indicating the presence of the class and zero indicating its absence. Further details about classes and their frequency is available in the appendices.
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

Due to constraints from the XGBoost library region could only be incorporated as a one-hot-encoded variable when used as a predictor. To better show what variables were related to region overall, another XGBoost tree was created with Region as the predicted value. The difference for this model was that relative variable importance would only be measured for each region specifically, as opposed to a variables overall importance in determining region. Separately profit (the difference between revenue and operational costs) and year was looked at in prior analyses (see appendix) but these results were not included due to low average loss values and model stability. 

@@

XGBoosted trees are an ensemble method that combines multiple decision trees together to create a more accurate predictive model. The gradient boosting aspect of the ensemble is the use of a loss function used to create new decision trees that add to the ensemble. Each new tree created is done so using a loss function that is optimised iteratively to improve upon prior tree's predictive power. The loss function can be any convex function, allowing gradient descent to traverse the loss space until, no improvements can be made via traversal. Because the loss function is only required to be convex, both classifiers and regressors can be used. Regularisation methods can also be incorporated to help prevent over fitting.

@@

The Sankey and Chord diagrams were constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Both Chord and Sankey diagrams illustrated variable importance through the size of the bands between two variables. The number at the end of a connection in a Sankey diagram indicates a variable's importance, or the number of times it appeared within the ensemble. Sankey and Chord  diagrams are presented together; with Sankey diagrams showing the connection of a variable to its ten most important predictor variables. Chord diagrams were used alongside a Sankey diagram to show the interconnectedness of the ten most prominent variables within its associated Sankey diagram. Chord diagrams formed circles, with variables being connected through their relative importance. The importance values for the Chord diagrams were taking from the models of those individual variables, with the diagram being simplified to just the ten variables in the associated Sankey diagram, for readability's sake.

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{revenue.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting revenue using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:revenue_sankey}
 \end{figure}

The prediction of revenue performed similarly to operating cost achieving an $R^2$ of 0.7716 (with a standard deviation of 0.1525). The value of predictors' relative importance was then calculated through the number of nodes used within the XGBoost. Values for relative importance were then used to construct Sankey and Chord diagrams to compare the contribution of each variable to predicting revenue.
\par
In order of importance, predictors of revenue were fuel use(petrol 307 and diesel 144), yield (285), size (216) and water use (199). Here, the values in the brackets indicate the relative importance of each variable (see \ref{fig:revenue_sankey}). Overall regions contributed to 234 nodes in the ensemble making them collectively the third most important variable. The chord diagram illustrates that vineyard area is also of high relative importance to other variables especially slashing. The overall importance of area to other variables is evident by its larger circumference within the chord diagram (see B in Figure \ref{fig:revenue_sankey}).
% The strong relationship of vineyard area to revenue and its predictors  but also has a high relative importance to the other predictors, The relation to area is likely to primarily be the effect of economies of scale, shown through its strong relations to other variables in figure \ref{fig:revenue_sankey}. Area harvested is likely also an indicator of other variables such as slashing passes its strongest connection presented.

@@

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Operating Costs using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:operating_costs_sankey}
 \end{figure}

Comparatively to revenue, operating cost performed better with the XGBoosted regression ensemble achieving an $R^2$ of 0.8025 (with a standard deviation of 0.1033). The relationships to operating cost through variable importance were found to be similar to that of revenue, with fuel, water, area and yield having the largest number relative importance (see figure \ref{fig:operating_costs_sankey}). A surprising difference is that the most important operational consideration for operating cost is the use of fungicide, compared to revenue where slashing is the most important (comparing Figure \ref{fig:region_sankey}). The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.
\par
Again, region played a determining factor overall, contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense.
\par
% . Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{region.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Region using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:region_sankey}
 \end{figure}

@@

\section{Discussion}

@@

Warmer regions are known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. In general warmer regions are not associated with higher yields, but if a vineyard in a warmer region is sufficiently irrigated much higher yields can be achieved than in cooler regions \citep{campsGrapeHarvestYield2012}. It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of grapes; reflected through region using water use so prominently in the XGBoost ensemble. The link to water resources in defining regions is also an important consideration, as vineyards can leverage higher irrigation rates given more accessible water resources. A further consideration in the link between revenue and region is that grape prices are set at a regional level by buyers \citep{wineaustraliaNationalVintageReport2022}. It is also important to consider that some regions carry particular fame regarding the quality of their produce such as Tasmania, the Hunter Valley and Barossa Valley \citep{hallidayAustralianWineEncyclopedia2009}. This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile (and thus quality) \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}.

@@

Separately revenue and operating cost did have a greater predictability than their counterpart profit. The disparity in accuracy between profit and other economic outcomes is reflective of the complexity in trying to address challenges such as climate change, disease and changing market demands \citep{wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022}. The difference between turning a profit or loss is dependent on predictable factors unforecasted factors, farming practice and farmers' decisions. The difference between vineyards that make profit and those that do not could be a multitude of factors including differences in farming practices not captured within this study. Some decisions leading to latent effects such as large scale soil deposition in extreme rain events can be caused by soil compaction due to overworking a vineyard \citep{capelloPermanentCoverSoil2020}.

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting revenue using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:revenue_sankey}
 \end{figure}

>>>>

\begin{abstract}

  The Australian wine industry is a major part of Australia's agricultural sector. As global demands change and new pressures on the industry present themselves, a more sustainable approach is needed. Through a nationwide data set, collected over ten years we link key variables in determining vineyard operational costs and revenue through the use of XGBoosted ensembles. We use the measure of relative importance to show the interrelated nature of these variables and the comparative influence they have on one another. We present these connections through the use of Sankey and Chord diagrams to show the important predictors of revenue and operating costs and how highly interrelated these variables are to one another. Furthermore, we connect these variables to different wine regions highlighting the complex interrelatedness of how location effects the use of different resources. The study provides valuable insights into the multifaceted dynamics governing operational costs and revenue illustrating how factors such as water and fuel use impacts operational costs and how different seasonal events affect these operations.

\end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

@@

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to support grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \small
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{Number of Classes} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & KGs of Nitrogen & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
\normalsize
The data originally contained only two multiclass variables: year and region. Related binary variables, such as the use of river water and the use of dam water, were combined to create multiclass variables such as water source for this example (see Appendix for further details). This was done by first converting each combination that occurred into its own unique category (such as river and damn water used, as opposed to two individual and separate categories). These variables were then one-hot-encoded, changing each variable class into a binary value, with one indicating the presence of the class and zero indicating its absence. Further details about classes and their frequency is available in the appendices.
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

Due to constraints from the XGBoost library region could only be incorporated as a one-hot-encoded variable when used as a predictor. To better show what variables were related to region overall, another XGBoost tree was created with Region as the predicted value. The difference for this model was that relative variable importance for each variable would be measured for the overall importance in determining region, as opposed to a variables connection to each region specifically. Separately profit (the difference between revenue and operational costs) and year were looked at in prior analyses (see appendix) but these results were not included due to low average loss values and model stability.

@@

XGBoosted trees are an ensemble method that combines multiple decision trees together to create a more accurate predictive model. The gradient boosting aspect of the ensemble is the use of a loss function used to create new decision trees that add to the ensemble improving its predictive power. Each new tree created is done so using a loss function that is optimised iteratively to improve upon prior tree. The loss function can be any convex function, allowing gradient descent to traverse the loss space until, no improvements can be made via traversal. Because the loss function is only required to be convex, both classifiers and regressors can be used. Regularisation methods can also be incorporated to help prevent over fitting. This makes XGBoosted trees incredibly versatile and accurate, whilst still being interpretable compared to other machine learning methods.

@@

The Sankey and Chord diagrams were constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Both Chord and Sankey diagrams illustrated variable importance through the size of the bands between two variables. The number at the end of a connection in a Sankey diagram indicates a variable's importance, or the number of times it appeared within the ensemble. Sankey and Chord  diagrams are presented together; with Sankey diagrams showing the connection of a variable to its ten most important predictor variables. Chord diagrams were used alongside the Sankey diagrams to show the interconnectedness of the ten most prominent variables within its associated Sankey diagram. Chord diagrams formed circles, with variables being connected through their relative importance. The importance values for the Chord diagrams were taking from the models of those individual variables, with the diagram being simplified to just the ten variables in the associated Sankey diagram, for readability's sake.

@@

The prediction of revenue performed similarly to operating cost achieving an $R^2$ of 0.7716 (with a standard deviation of 0.1525). The value of predictors' relative importance was then calculated through the number of nodes used within the XGBoost. Values for relative importance were then used to construct Sankey and Chord diagrams to compare the contribution of each variable in predicting revenue.
\par
In order of importance the predictors of revenue were fuel use (petrol 307 and diesel 144), yield (285), size (216) and water use (199). Here, the values in the brackets indicate the relative importance of each variable (see \ref{fig:revenue_sankey}). Overall regions contributed to 234 nodes in the ensemble making them collectively the third most important variable. The chord diagram illustrates that vineyard area is also of high relative importance to other variables especially slashing. The overall importance of area to other variables is evident by its larger circumference within the chord diagram (see B in Figure \ref{fig:revenue_sankey}).
% The strong relationship of vineyard area to revenue and its predictors  but also has a high relative importance to the other predictors, The relation to area is likely to primarily be the effect of economies of scale, shown through its strong relations to other variables in figure \ref{fig:revenue_sankey}. Area harvested is likely also an indicator of other variables such as slashing passes its strongest connection presented.

\begin{figure}[htb]
  \label{fig:revenue_sankey}
  \resizebox{\textwidth}{!}{
  \includegraphics{revenue.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting revenue using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}
 \end{figure}

@@

Comparatively to revenue, operating cost performed better with the XGBoosted regression ensemble achieving an $R^2$ of 0.8025 (with a standard deviation of 0.1033). The relationships to operating cost through variable importance were found to be similar to that of revenue, with fuel, water, area and yield having the largest number relative importance (see figure \ref{fig:operating_costs_sankey}). A surprising difference was the change in relative importance of activities involving tractors passes where the use of fungicide was more important for operational costs, compared to revenue, where slashing was more important (comparing Figure \ref{fig:region_sankey}). The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.
\par
Again, region played a determining factor overall, contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense.
\par
% . Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).
\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Operating Costs using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:operating_costs_sankey}
 \end{figure}

@@

@@

\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{region.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Region using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:region_sankey}
 \end{figure}
\section{Discussion}

@@

Warmer regions are known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. In general warmer regions are not associated with higher yields, but if a vineyard in a warmer region is sufficiently irrigated much higher yields can be achieved than in cooler regions \citep{campsGrapeHarvestYield2012}. It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of grapes; reflected through region using water use so prominently in the XGBoost ensemble. The link to water resources in defining regions is also an important consideration, as vineyards can leverage higher irrigation rates given more accessible water resources. A further consideration in the link between revenue and region is that grape prices are set at a regional level by buyers \citep{wineaustraliaNationalVintageReport2022}. It is also important to consider that some regions carry particular fame regarding the quality of their produce such as Tasmania, the Hunter Valley and Barossa Valley \citep{hallidayAustralianWineEncyclopedia2009}. This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}.

@@

Separately revenue and operating cost did have a greater predictability than their counterpart profit (see appendix). The disparity in accuracy between profit and other economic outcomes is reflective of the complexity in trying to address challenges such as climate change, disease and changing market demands \citep{wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022}. The difference between turning a profit or loss is dependent on predictable factors unforecasted factors, farming practice and farmers' decisions. The difference between vineyards that make profit and those that do not could be a multitude of factors including differences in farming practices not captured within this study. Some decisions leading to latent effects such as large scale soil deposition in extreme rain events can be caused by soil compaction due to overworking a vineyard \citep{capelloPermanentCoverSoil2020}.

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting revenue using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:profit}
 \end{figure}
